---
title: "Examples mark 2"
output: html_notebook
---
# Header 1
## Header 2
### Header 3
This is generic text that you can use.
If you want to do r code within the text, you use ` then you use the letter r, enter the r code, then end with another accent (not included), and the text will run.
```{r}
summary(iris)
summary(iris$Sepal.Length)
fivenum(iris$Sepal.Length)
```

For example, the median of the sepal length is `r median(iris$Sepal.Length)`

The basic commands for adding labels to a graph are:

main = "text here" this is the title for the graph
xlab = "text here" this is the x label text. AKA words at the bottom of the graph
ylab = "text here" this is the y label text. AKA words at the side of the graph
col = "color here" or col = c("First color", "Second Color", "etc") for the colors
freq = TRUE will give counts, freq = FALSE will give base percentage

I'm being fancy, so I made a density plot.
Density is calculated using the density function. I created a variable called density.sepal.length and added to it using <-
The command is density(dataset$variable)

I added to the histogram by using the lines(density.sepal.length). I then added a color line by using col = "Gold"

```{r}
hist(iris$Sepal.Length, main = "Histogram of Sepal Length", xlab= "Sepal Length", ylab = "Frequency", col = "Purple", freq=FALSE)
density.sepal.length<-density(iris$Sepal.Length)
lines(density.sepal.length, col = "Gold")
```

I could also do the density by itself by plotting density. But then you would have to add a new title, xlab, ylab, and color.
```{r}
plot(density.sepal.length)
```


The first thing to do with a pie chart is to create a table of the data. You need this because you need count data to make these charts. Iris is kinda boring, but it's my example.

The command is:
table(dataset$variable)

Make sure you are looking at your classification. 

To make your percentages, you can use a function called prop.table using the sytax:

prop.table(table.name)

So, I took everything and multipled it by 100. I also used the function round to round to zero digits.

I will create a variable called titles, and name them Three Gears, Four Gears, and Five Gears using the command
titles<-c("Three Gears", "Four Gears", "Five Gears")

I will then use the paste function to combine the percentages and the titles into another variable called lbl.gear

The syntax is:

lbl.gear<-paste(titles, percentage)

The pie function creates the pie chart. We will use the gear.mtcars to make the chart and the lbl.gear to add the labels.

Then we add the title and colors as we want.
```{r}
gear.mtcars<-table(mtcars$gear)
percentage<-round(prop.table(gear.mtcars)*100, digits=0)
titles<-c("Three Gears", "Four Gears", "Five Gears")
lbl.gear<-paste(titles, percentage)
pie(gear.mtcars, labels=lbl.gear)
```

Now for the bar plot. This is easier, especially now that we have done that.

I used the gear.mtcars, which is based off of a table, and ran that in the function barplot.

barplot(gear.mtcars)

Then you add colors, title, and labels as above.
```{r}
barplot(gear.mtcars)
```
The last one is the boxplot. This finally looks at mpg a little more. So, since I already have made people not use gears, I'll use it here.

We use the ~ key to add a factor to the boxplot. This will breaks down the boxplot into different categories. This will allow you to see how the gears, in this case, affects the mpg. Here, 4 and 5 gears have a higher mpg than 3, and maybe significantly so.

And we can add the title et al later.
```{r}
boxplot(mtcars$mpg~mtcars$gear)
```

