---
title: "Project 2 Example"
output:
  pdf_document: default
  html_notebook: default
---

# Figuring out the number of bets
So, the first thing I want to do is to figure out the number of bets I will make per amount.

Note, when I want to find out the total number of bets, I need to use the code %/% to find the total number of bets because I cannot have partial bets.
```{r}
amount.won<-2000
bet.amount<-c(1,5,10,20,40,60,80,100,120,140,160,180,200)
total.bets<-amount.won %/% bet.amount
total.bets
```

So, now we need to find out how much money we can win based on all of these.

So, I will calcualte this based off of a street bet (any three numbers in a row ex: 1, 2 or 3). I need to do some math.
The odds to win are 17 to 1, so you take the total number of bets and divide by 17 to get the total number of wins.

However, you can't have a partial win, so you need to use the function %/% to divide and round down. From there, you need to multiply it by the amount bet and by the payout. The payout for this is 11 2/3 to 1
```{r}
wins<-total.bets%/%17
payout<-bet.amount*11.67
amount.won<-wins*payout
roi<-amount.won/2000*100
wins
amount.won
roi
```

To find the confidence interval, you can use the function qnorm

```{r}
error<-qnorm(.975)/1*total.bets
error
left<-amount.won-error
right<-amount.won+error
left
right
```

However, we can't have a negative amount won given that you can't lose free money. So our amount won is between 0 and $5285.32
